---
title: "Check that images were downloaded"
author: "Joshua Cook"
date: "2019-09-09"
output:
    html_document:
        toc: true
        theme: paper
        includes:
            in_header: header.html
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    comment = "#>"
)
library(tidyverse)

EXPECTED_NUMBER_OF_IMAGES <- 300
```
This document contains a summary of the photos downloaded for the plants.

## Plants

```{r}
plant_dirs <- list.dirs("images", )[-1] %>% unlist()
plant_names <- basename(plant_dirs) %>% unlist()
plant_list <- readLines("plant_names.txt") %>%
    str_replace(" ", "_") %>%
    unlist()
```

```{r}
count_files_in <- function(dir_path) {
    purrr::map_int(dir_path, ~ length(list.files(.x)))
}

images_tib <- tibble(dir = plant_dirs, name = plant_names) %>%
    mutate(num_files = count_files_in(dir_path = dir))
```

### Summary Stats

Number of plants expected: `r n_distinct(plant_list)`  
Number of plants with directory: `r n_distinct(plant_names)`  
Mean number of images: `r round(mean(images_tib$num_files), 2)`  
Median number of images: `r round(median(images_tib$num_files), 2)`  
Min./max. number of images: `r min(images_tib$num_files)` / `r max(images_tib$num_files)`  
Number of files with less than the expected number of images: `r sum(images_tib$num_files < EXPECTED_NUMBER_OF_IMAGES)`

```{r}
images_tib %>%
    mutate(plant_names = fct_reorder(name, -num_files)) %>%
    ggplot(aes(x = plant_names, y = num_files)) +
    geom_col(color = "dodgerblue") +
    scale_y_continuous(expand = expand_scale(mult = c(0, 0))) +
    theme_bw() +
    theme(
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
    ) +
    labs(
        x = "plant",
        y = "number of images",
        title = "Number of images for each plant"
    )
```

```{r}
if (any(images_tib$num_files < EXPECTED_NUMBER_OF_IMAGES)) {
    images_tib %>%
        filter(num_files < EXPECTED_NUMBER_OF_IMAGES) %>%
        mutate(name = str_replace_all(name, "_", " "),
               plant_names = fct_reorder(name, -num_files)) %>%
        ggplot(aes(x = plant_names, y = num_files)) +
        geom_col(fill = "dodgerblue") +
        scale_y_continuous(expand = expand_scale(mult = c(0, 0))) +
        theme_bw() +
        theme(
            plot.title = element_text(hjust = 0.5),
            axis.text.x = element_text(angle = 50, hjust = 1.0, size = 5),
            axis.title.x = element_blank()
        ) +
        labs(
            y = "number of images",
            title = paste0("Number of images for plants with fewer than expected (", EXPECTED_NUMBER_OF_IMAGES, ")")
        )
}
```

```{r}
failed_download_plants <- images_tib %>%
    filter(num_files < EXPECTED_NUMBER_OF_IMAGES) %>%
    pull(name)
if (length(failed_download_plants) > 0) {
    cat(failed_download_plants, file = "failed_dwnlds_plant_names.txt", sep = "\n")
}
```

There were `r length(failed_download_plants)` saved to "failed_dwnlds_plant_names.txt". These can be re-run using the following command:

```bash
sbatch --array=1-$(wc -l < failed_dwnlds_plant_names.txt) download_google_images.sh failed_dwnlds_plant_names.txt
```


## Images

```{r}
image_sizes <- list.files("images", recursive = TRUE, full.names = TRUE) %>%
    file.size() %>%
    gdata::humanReadable(units = "K", standard = "Unix") %>%
    str_remove(" K") %>%
    as.numeric()
tibble(img_size = image_sizes / 1e3) %>%
    ggplot(aes(x = img_size)) +
    geom_density(color = "black", fill = "grey50") +
    scale_y_continuous(expand = expand_scale(mult = c(0, 0.02))) +
    scale_x_continuous(expand = expand_scale(mult = c(0, 0.02)), breaks = c(1:100)) +
    theme_bw() +
    theme(
        plot.title = element_text(hjust = 0.5)
    ) +
    labs(
        x = "image file size (MB)",
        y = "density",
        title = "Distribution of image file sizes"
    )
```

### Summary Stats

Total number of images: `r length(image_sizes)`  
Total storage space: `r round(sum(image_sizes) / 1e3, 2)` MB  
Mean image size: `r round(mean(image_sizes) / 1e3, 2)` MB  
Median image size: `r round(median(image_sizes) / 1e3, 2)` MB  
Min./max. image size: `r round(min(image_sizes) / 1e3, 2)` MB / `r round(max(image_sizes) / 1e3, 2)` MB

---

## Session Info

```{r}
sessionInfo()
```